Higher-Order unification for free!

### 2024-04-11 paper/main.tex
update sec maybebeta0

\paragraph{Detection} trivial, pattern-fragment.
\subsection{Compilation and decompilation}

The following rule is inserted just before rule~\ref{rule:compapp}.

@@

\paragraph{Decompilation} since no link, nothing new

\paragraph{Progress} since ML unif is complete here, no
need to move terms aside, just use uva is enough.

>>>>

A first problem we encounter when making unification between terms that are
well behaved is the need to treat higher-order variables. 
%
% make test ONLY=7006 TEX=tex
\printAlll
  {{{\lambda x.(f\appsep (X\appsep x)\appsep a),\lambda x.(f\appsep x\appsep a)}}}
  {{{\lambda x.(f\appsep (A\appsep x)\appsep a),\lambda x.(f\appsep x\appsep a)}}}
  {{{X,A,0}}}
  {{}}

In the example above, we can note that the very basilar compilation given in 
the previous section is not able to make the \Ho unification problem succeeds.
The unification of $T_1$ fails while trying to unifying $A \appsep x$ and $x$.
This is due to the fact that $A \appsep x$ (equivalent to \elpiIn{app[uva A [], x]})
is represented as the application of the variable $A$ to the name $x$.
In order to exploit the higher-order unification algorithm of the meta language,
we need to compile the \Fo{} term $X\appsep x$ into the \Ho term $A_x$.

In order to address this problem, we add the following rule before rule~\ref{rule:compapp}.

@@

\paragraph{Decompilation} Since no link is created by the compilation of 
\maybebeta terms, no modification should be done
to the \elpiIn{commit-link} predicate.

\paragraph{Progress} Similarly to decompilation, since no link is produced,
no modification to the \elpiIn{progress} predicate is needed.
